[dcpo_demsupport]

### 2020-06-06 paper/dcpo_demsupport.Rmd
fuss with packages: add modelsummary for tables, drop purrr (in tidyverse) and broom (in modelsummary)

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, # analysis
  huxtable, kableExtra, # tabulation
  latex2exp, # visualization
  purrr, broom, tidyverse
) # data wrangling # data wrangling

>>>>

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  latex2exp, # visualization
  tidyverse # data wrangling
)
